---
output: md_document
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

<!-- Badges -->
[![CRAN Version](https://img.shields.io/cran/v/miselect?style=flat-square&color=blue&label=CRAN)](https://cran.r-project.org/package=miselect)
[![GitHub Release](https://img.shields.io/github/v/release/umich-cphds/miselect?include_prereleases&label=Github&style=flat-square&color=blue)](https://github.com/umich-cphds/miselect)
[![Travis CI](https://img.shields.io/travis/umich-cphds/miselect?style=flat-square)](https://travis-ci.org/umich-cphds/mianet)

# Variable Selection for Multiply Imputed Data

Penalized regression methods, such as lasso and elastic net, are used in
many biomedical applications when simultaneous regression coefficient
estimation and variable selection is desired. However, missing data
complicates the implementation of these methods, particularly when
missingness is handled using multiple imputation. Applying a variable selection
algorithm on each imputed dataset will likely lead to different sets of selected
predictors, making it difficult to ascertain a final active set without
resorting to ad hoc combination rules. 'miselect' presents Stacked Adaptive
Elastic Net (saenet) and Grouped Adaptive LASSO (galasso) for continuous and
binary outcomes. They, by construction, force selection of the same variables
across multiply imputed data. 'miselect' also provides cross validated variants
of these methods.

## Installation

`miselect` can installed from Github via
```{r, eval = F}
# install.packages("devtools")
devtools::install_github("umich-cphds/miselect", build_opts = c())
```
The Github version may contain bug fixes not yet present on CRAN,
so if you are experiencing issues, you may want to try the Github
version of the package.

## Example

Here is how to use cross validated `saenet`. A nice feature of `saenet`
is that you can cross validate over `alpha` without having to use `foldid`.

```{r}
library(miselect)
library(mice)

set.seed(48109)
# Using the mice defaults for sake of example only.
mids <- mice(miselect.df, m = 5, printFlag = FALSE)
dfs <- lapply(1:5, function(i) complete(mids, action = i))

# Generate list of imputed design matrices and imputed responses
x <- list()
y <- list()
for (i in 1:5) {
    x[[i]] <- as.matrix(dfs[[i]][, paste0("X", 1:20)])
    y[[i]] <- dfs[[i]]$Y
}

# Calculate observational weights
weights  <- 1 - rowMeans(is.na(miselect.df))
pf       <- rep(1, 20)
adWeight <- rep(1, 20)
alpha    <- c(.5 , 1)

# Since 'Y' is a binary variable, we use 'family = "binomial"'
fit <- cv.saenet(x, y, pf, adWeight, weights, family = "binomial",
                 alpha = alpha)

# By default 'coef' returns the betas for (lambda.min , alpha.min)
coef(fit)
```
You can supply different values of `lambda` and `alpha`. Here we use the
`lambda` and `alpha` selected by the one standard error rule
```{r}
coef(fit, lambda = fit$lambda.1se, alpha = fit$alpha.1se)
```
## Bugs
If you encounter a bug, please open an issue on the [Issues](https://github.com/umich-cphds/miselect/issues)
tab on Github or send us an email.

## Contact
For questions or feedback, please email Jiacong Du at
<jiacong@umich.edu> or Alexander Rix <alexrix@umich.edu>.

<!-- ## References -->
