---
title: "Variable Selection for Multiply Imputed Data"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{miselect}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Penalized regression methods, such as lasso and elastic net, are used in
many biomedical applications when simultaneous regression coefficient
estimation and variable selection is desired. However, missing data
complicates the implementation of these methods, particularly when
missingness is handled using multiple imputation. Applying a variable selection
algorithm on each imputed dataset will likely lead to different sets of selected
predictors, making it difficult to ascertain a final active set without
resorting to ad hoc combination rules. 'miselect' presents Stacked Adaptive
Elastic Net (saenet) and Grouped Adaptive LASSO (galasso) for continuous and
binary outcomes. They, by construction, force selection of the same variables
across multiply imputed data. 'miselect' also provides cross validated variants
of these methods.

`saenet` works by stacking the multiply imputed data into a single matrix and
running a weighted adaptive elastic net on it. `galasso` works by adding a
group penalty to the aggregated objective function to ensure selection
consistency across imputations. Simulations suggest that the "stacked"
objective function approach (i.e., `saenet`) tends to be more computationally
efficient and have better estimation and selection properties.

## Installation

`miselect` can installed from Github via
```{r, eval = F}
# install.packages("devtools")
devtools::install_github("umich-cphds/miselect", build_opts = c())
```
The Github version may contain bug fixes not yet present on CRAN,
so if you are experiencing issues, you may want to try the Github
version of the package.

## Example

The purpose of this example is to help the user get started with using the
methods in the package. To facilitate this, we have included a synthetic
example dataset in the package, `miselect.df`, which contains a binary response,
`Y` and 20 continuous covariates, `X[1-20]`.

```{r}
library(miselect)

colMeans(is.na(miselect.df))
```

As you can see, this dataset includes missing values, so we need to impute it
using the R package `mice`. Imputation should be done carefully to avoid
creating biases in the imputed data that could affect the actual analysis of
interest. There are many tutorials available on how to do this properly, but a
good reference text is (Little and Rubin 2019).

However, for the sake of example, we are going to just use the default `mice`
settings, i.e., predictive means matching.
```{r}
library(mice)

set.seed(48109)

# Using the mice defaults for sake of example only.
mids <- mice(miselect.df, m = 5, printFlag = FALSE)
```

Both `saenet` and `galasso` take lists of (imputed) design matrices and
responses. Manipulating the mice output into this form is not too difficult.
```{r}
# Generate list of completed data.frames
dfs <- lapply(1:5, function(i) complete(mids, action = i))

# Generate list of imputed design matrices and imputed responses
x <- list()
y <- list()
for (i in 1:5) {
    x[[i]] <- as.matrix(dfs[[i]][, paste0("X", 1:20)])
    y[[i]] <- dfs[[i]]$Y
}

```

```{r}
# Calculate observational weights
weights  <- 1 - rowMeans(is.na(miselect.df))
pf       <- rep(1, 20)
adWeight <- rep(1, 20)
alpha    <- c(.5 , 1)

# Since 'Y' is a binary variable, we use 'family = "binomial"'
fit <- cv.saenet(x, y, pf, adWeight, weights, family = "binomial",
                 alpha = alpha, nfolds = 5)

# By default 'coef' returns the betas for (lambda.min , alpha.min)
coef(fit)
```
`coef`, by default, returns the coefficients for the `lambda` / `alpha`
that has the lowest cross validation error.

You can supply different values of `lambda` and `alpha`. Here we use the
`lambda` and `alpha` selected by the one standard error rule
```{r}
coef(fit, lambda = fit$lambda.1se, alpha = fit$alpha.1se)
```

Note that the adaptive weights (`adWeight`) are all `1`, so `fit` was just an
elastic net. Let's use the coefficients from it as adaptive weights. The first
term is the intercept, so we drop it.

```{r}
adWeight <- 1 / (abs(coef(fit)[-1]) + 1 / nrow(miselect.df))

afit <- cv.saenet(x, y, pf, adWeight, weights, family = "binomial",
                  alpha = alpha, nfolds = 5)

coef(afit)
```

`galasso` works similarly to `saenet`, but does not have `weights`, or `alpha`
parameters.

## Bugs
If you encounter a bug, please open an issue on the [Issues](https://github.com/umich-cphds/miselect/issues)
tab on Github or send us an email.

## Contact
For questions or feedback, please email Jiacong Du at
<jiacong@umich.edu> or Alexander Rix <alexrix@umich.edu>.

## References

Little, R. J., & Rubin, D. B. (2019). Statistical analysis with missing data
(Vol. 793). John Wiley & Sons.
